% Ian Kronquist's Resume
% Copyright 2015

\documentclass[11pt]{article}
\topmargin=0.0in
\textwidth=6.5in

\topmargin 0pt
\advance \topmargin by -\headheight
\advance \topmargin by -\headsep

\setlength{\hoffset}{-0.25in}

\oddsidemargin 0pt
\evensidemargin \oddsidemargin
\marginparwidth 0.5in


\headheight=0pt
\headsep=0pt
\textheight=10.5in

\pagenumbering{gobble}
\setlength{\parindent}{0pt}

\usepackage[normalem]{ulem} % for the underlines
\usepackage[compact]{titlesec}

\newcommand{\heading}[1]{
    \section*{\uline{#1 \hfill}}
}

\newcommand{\squish}{
    \setlength{\itemsep}{0.5pt}
    % tweak parskip value to adjust size on page
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.5pt}
}

% naming it 'date' would conflict with builtins
\newcommand{\when}[1]{
    \hfill \emph{#1}
}

% place, optional title, date
\newcommand{\experience}[3]{
    \ifx&#2&
        \item[{#1}]
    \else
        \item[{#1}, \emph{#2}]
    \fi
    \when{#3}\\
}

\newcommand{\contact}[5]{
    \centerline{
        \large
        \texttt{#1}
        $\bullet$
        \texttt{#2}
    }
	\centerline{
        \texttt{#3}
        $\bullet$
		\texttt{#4}
	}

}

\newcommand{\skill}[2]{
    \textbf{#1} \hspace{5 mm} #2 \hfill \\
}

\newcommand{\project}[2]{
    \textbf{#1} \hfill #2 \\
}


\begin{document}

\centerline{{\LARGE \bf Ian Kronquist}}
\vspace{3ex}

\contact{iankronquist@teleport.com}
        {260 Pine Valley Road, Lake Oswego, Oregon}
		{971 222 5148}
		{github.com/iankronquist}

\heading{Skills}
\begin{tabular}{ @{} l @{\hspace{6ex}} l }
\textbf{Development} & Python, C/C++, Ruby, Chef, Puppet, Docker, Git, GitHub, Javascript, Django \\
\textbf{Leadership} & Curriculum Design, Teaching, Public Speaking \\
\end{tabular}

\heading{Employment}
\begin{description}
\squish

\experience{Puppet Labs, Puppet Language Design Team}
           {Engineering Intern}
           {June 2015-Present}
		Implemented a tool to generate HTML documentation from code comments.
		Designed and prototyped a system for instrumenting the Puppet parser to
		extract test coverage statistics. Implemented built-in functions for
		the Puppet catalog compiler.

\experience{Oregon State University Open Source Lab}
           {Developer}
           {November 2013-Present}
		Wrote a web back end for the lab's NodeJS time management API.
		Wrote Docker development environments and DevOps Chef cookbooks for
		deploying the lab's Python web applications.
		Used NodeJS, Javascript, Python, Django, Flask, Docker, and Chef.

\experience{Mozilla, SUMO Engineering Team}
           {Intern}
           {June-September 2014}
		Designed and implemented a Bayesian spam and abuse detection and
		filtering library in python for Mozilla's user input Django site.

\experience{Reach Technology}
           {Intern}
		   {July-September 2013}
		Wrote a cross-platform C++ desktop application for the customer
		development kit for an embedded graphics display module. Wrote the
		company product wiki and documentation. Created customer video
		tutorials.

\end{description}

\heading{Leadership}
\begin{description}
\squish
	\experience{Eagle Scout}{}{}
		Designed, constructed, and gathered donations for a lending library
		for a disadvantaged community in North-East Portland as an Eagle
		Project.

	\experience{DevOps BootCamp}{}{}
		Designed a curriculum and taught core software development and systems
		operation skills to OSU students.

\end{description}

\heading{Education}
\squish
\begin{description}
\squish
	\experience{Oregon State University}
	           {Corvallis, Oregon.}
			   {Current Student}
		Pursuing a Dual Degree Bachelor of Science, Computer Science,
		and Bachelor of Science, Mathematics.
		Honors College student. Senior standing, expected graduation Summer
		2016.  GPA: 3.71.

	\experience{AFS Turkey Foreign Exchange Program}
               {Adana, Turkey.}
			   {September 2012-July 2013}
		Attended G{\" u}ndo{\u g}du Koleji (Sunrise High School) in Adana,
		Turkey. Proficient in the Turkish Language.

	\experience{Portland Community College}
	           {Portland, Oregon}
			   {June, 2012}
		Graduated with Honors with an Associates of Arts
		Oregon Transfer degree.
\end{description}

\heading{Projects and Notable Open Source Contributions}
\begin{tabular}{ @{} l @{\hspace{6ex}} l }
\textbf{MyPy} & Static type checking for Python. Fixed parsing errors,
	removed outdated systems. \\
\textbf{Hope JIT} & A Python JIT for astronomical computations. Modified codegen
to work on OS X. \\
\textbf{Kernel of Truth} & Personal project implementing a i586 C kernel written
	from scratch. \\
\end{tabular}

\end{document}
